Plots_Genome

### 2025-07-14 Code/Plots_Genome.Rmd
trimmed version of Prochlorococcus O2 genome plot

>>>>

```{r ProchlorococcusEnzymeKmsTrim, fig.cap=ProchlorococcusEnzymeKmsTrim_cap, fig.height=10, fig.width=20, message=FALSE, warning=FALSE}

ProchlorococcusEnzymeKmsTrim_cap <- glue("**Comparison of log~10~(K~m~ for O~2~ in mM) vs.genes encoding O~2~ utilizing enzymes in *Prochlorococcus***, faceted by their respective strains.",
                                     "Symbol color corresponds to number of genes encoding O~2~ utilizing enzymes.",
                                     "Symbol shape corresponds to whether the K~m~ was measured in the respective enzyme, or inferred from the K~m~ of a similar enzyme.",
                                     "Black vertical line corresponds to the range of K~m~ for O~2~.",
                                     "Vertical translucent bars correspond to concentrations of O~2~ in which *Prochlorococcus* strains were grown.",
                                     "K~m~ values were obtained from other organisms, excluding Ribulose bisphosphate carboxylase.",
                                     "Symbol absence means no sequences were detected in the genome."
                                     )

ProchlorococcusEnzymeKmsTrim <- MergedData %>%
  filter(!is.na(Gene_count),
         Genus == "Prochlorococcus",
         # Strain %in% c("CCMP1986", "MIT9313"),
         Strain %in% c("CCMP1986", "MIT9313"),
         !is.na(Estimated),
         Taxa == "Prokaryote",
         EnzymeName %in% c("decaprenylphospho-beta-D-ribofuranose 2-dehydrogenase", "ubiquinol oxidase (non-electrogenic)","acireductone dioxygenase (Ni2+-requiring)", "(S)-2-hydroxy-acid oxidase", "bacterial non-heme ferritin")) %>% 
  mutate(StrainLabel = case_when(Strain == "CCMP1375" ~ "SS120",
                                 Strain == "CCMP1986" ~ "MED4",
                                 Strain == "MIT9313" ~ "MIT9313",
                                 Strain == "NATL2A" ~ "NATL2A")) %>%
  mutate(StrainLabel = factor(StrainLabel, levels = c("MED4", "NATL2A", "SS120", "MIT9313"))) %>%
  group_by(EC) %>%
  mutate(Km_mM_min = min(Km_mM, na.rm = TRUE), 
         Km_mM_max = max(Km_mM, na.rm = TRUE),
         Gene_count = as.character(Gene_count)) %>%
  # mutate(Km_mM = case_when(Genus == "Prochlorococcus" & EC == "4.1.1.39" ~ 1.4,
  #                          TRUE ~ Km_mM),
  #        Km_mM_min = case_when(Genus == "Prochlorococcus" & EC == "4.1.1.39" ~ 1.4,
  #                          TRUE ~ Km_mM_min),
  #        Km_mM_max = case_when(Genus == "Prochlorococcus" & EC == "4.1.1.39" ~ 1.4,
  #                          TRUE ~ Km_mM_max)) %>% 
  # mutate(Km_mM = case_when(EnzymeName == "Flavodiiron (Flv1a/3a)" ~ 10/1000,
  #                          TRUE ~ Km_mM)) %>% 
  ungroup() %>% 
    mutate(EnzymeName_bold = case_when(EnzymeName %in% c("(S)-2-hydroxy-acid oxidase", "ubiquinol oxidase (non-electrogenic)") ~ glue("<b>{EnzymeName}</b>"),
                                     TRUE ~ EnzymeName))

 (ProchlorococcusEnzymeKmsTrimPlot <- ProchlorococcusEnzymeKmsTrim %>%
  ggplot() +
  geom_errorbar(aes(x = reorder(EnzymeName_bold, Km_mM * 1000), ymin = Km_mM_min* 1000, ymax = Km_mM_max* 1000)) +
  annotate(geom = "rect", ymin = (5e-4 * 1000), ymax =  (5e-3 * 1000), xmin = -Inf, xmax = Inf, alpha = 0.3, fill = "blue") +
  annotate(geom = "rect", ymax = (5e-2 * 1000), ymin =  (5e-3 * 1000), xmin = -Inf, xmax = Inf, alpha = 0.3, fill = "green") +
  annotate(geom = "rect", ymax = (280e-3 * 1000), ymin =  (230e-3 * 1000), xmin = -Inf, xmax = Inf, alpha = 0.3, fill = "#FF0000") +
  geom_point(aes(x = reorder(EnzymeName_bold, Km_mM* 1000), y = (Km_mM* 1000), shape = as.logical(Estimated)), stroke = 1) +
  geom_vline(aes(xintercept = reorder(EnzymeName_bold, Km_mM* 1000)), size = 2,  data = . %>% filter(is.na(Km_mM)), linetype = "solid") +
  geom_text(aes(x = 5.3, y = 2.5, label = "≈2.5 µM [O2]"), color = "blue", size = 6) +
  geom_text(aes(x = 5.3, y = 25, label = "≈25 µM [O2]"), color = "darkgreen", size = 6) +
  geom_text(aes(x = 5.3, y = 250, label = "≈250 µM [O2]"), color = "#FF0000", size = 6) +
  ggh4x::facet_nested(rows = vars(StrainLabel)) +
  theme_bw() +
   ggpubr::rotate_x_text(angle = 80) + 
   scale_shape_manual(values = c(19,8), labels = c("FALSE" = "Measured", "TRUE" = "Inferred")) +
  scale_color_brewer(palette="Dark2") +
   labs(# title = ~K[m] ~O[2] ~  "for *Prochlorococcus* Enzymes using Oxygen", # "Estimates of Affinities of *Prochlorococcus* Enzymes for Oxygen" # "Affinities for Phytoplankton Enzymes for Oxygen", 
       x = "Enzyme name",
       y = ~K[m] ~O[2] ~"(µM)",
       size = "Gene count",
       shape = ""~K[m]) +
  scale_y_continuous(trans=scales::pseudo_log_trans(base = 10),
                     breaks=c(1, 10, 100, 1000, 10000, 100000)) +
   guides(shape = guide_legend(override.aes = list(size=5))) +
   theme(axis.title = element_text(size = 30, color = "black"),
          axis.title.x = element_text(vjust=8),
          title = element_text(size = 30),
         axis.text.y = element_text(size = 20, color = "black"),
         axis.text.x = ggtext::element_markdown(size = 18, color = "black"),
         strip.text = element_text(size = 30),
         legend.key.size = unit(2, 'cm'), #change legend key size
        legend.title =  element_text(size = 30),  #change legend title font size
        legend.text = element_text(size = 30))
 )
     #change legend text font size

```{r, ProchlorococcusEnzymeKmsTrimPlot ggsave, include = FALSE} 
ggsave(filename = file.path(Figures, "ProchlorococcusEnzymeKmsTrim.png"), plot = ProchlorococcusEnzymeKmsTrimPlot, height = 12, width = 17)
```
